Live and Let Die? (Delayed Issues not Harder to Resolve)

### 2016-06-15 phaseDelay.tex

This paper tests for the delayed issue effect in
171 software projects conducted around the world in the period from 2006--2014.
To the best of our knowledge,  this is the largest study
yet published on this effect.
In our sample, we found no evidence for the  delayed issue effect; i.e.
the  time  to resolve 
issues in a later phase was not consistently  more than  
when  issues were resolved soon after their introduction.

@@

\subsection{Observations from 171 Projects}

@@

On the other hand, a remarkable feature of Figure~\ref{fig:raw} is the {\em absence}
of an exponential delay effect during development.
In our data, the greatest increase in difficulty in resolving requirements issues was the 1.31 scale-up seen in systems testing--
which is far smaller than the 37 to 250-fold increases reported in \fig{b81}, \fig{cost-to-fix},
and \fig{steck}.  That is, from our  data, we would not anticipate exponentially greater difficulty in resolving requirements issues after
deployment. 
 \subsubsection{Comment 3}
 The above specific statements are related just to requirements. Turning now
 to issues created in all phases in Figure~\ref{fig:raw},  we see that
 this data does not follow the exponential increase predicted
by the delayed issue effect:
\bi
\item There is much ``up and down'' in the chart. 
\item If we separate out just the {\em Inspect} or {\em Review} data, we can see that there is some increase in {\em Design} and {\em Code}. However, that effect could be a linear or be just noise. In either case,
it does not look like exponential.
\item The time in final testing is particularly low suggesting that few defects survived into testing
(and hence, there were few instances where code required massive rework).
\ei
%In summary:
%\bi
%\item
%The delayed issue effect has been reported in around a dozen papers, at least half of which date back to the 1970s. 
%\item
%But there is no trace of that  effect   in hundreds of software projects built  since 2006.
%\ei
%For illustrative purposes, the relative cost to fix errors per lifecycle phase in the TSP project data is overlayed with Boehm's cost curve~\cite{Boehm81} as well as the CCPDS-R case study~\cite{Royce98} in \fig{cost-to-fix-tsp}. Cost-to-fix for TSP is total time spent in each review, inspection, or test-related phase / \# of defects found in phase (reported in \fig{raw}). It is clear to see that the trend is relatively flat, closer to the pattern exhibited by the Royce case study (which also focused on early defect removal) than the exponential growth curve.

@@

Having documented the above issues, we assert that they are unlikely to be major issues in the study.
As to the first point, that some debugging may be more expensive than others, one of us (Nichols)
was closely associated with many of the projects in our sample. He is unaware of any frequent
use of exorbitantly expensive tools or people on these projects. As to the second point (that
some defects have an impact beyond the mere cost to fix them), we have no evidence suggesting
that the net effect of this concern over all our projects is non-zero.

@@

\vspace*{0.5mm}
\scriptsize
\balance
\bibliographystyle{plain}
\bibliography{refs}

>>>>

This paper tests for the delayed issue effect in
171 software projects conducted around the world in the period from 2006--2014.
To the best of our knowledge,  this is the largest study
yet published on this effect.
We found no evidence for the  delayed issue effect; i.e.
the  time  to resolve 
issues in a later phase was {\bf not} consistently  more than  
when  issues were resolved soon after their introduction.

@@

\newpage
\subsection{Observations from 171 Projects}

@@

On the other hand, a remarkable feature of Figure~\ref{fig:raw} is the {\em absence}
of an exponential delay effect during development.
In our data, the greatest increase in difficulty in resolving requirements issues was the 1.31 scale-up seen in systems testing--
which is far smaller than the 37 to 250-fold increases reported in \fig{b81}, \fig{cost-to-fix},
and \fig{steck}.  That is, from our  data, we would not anticipate exponentially greater difficulty in resolving requirements issues after
deployment. 
 \subsubsection{Comment 3}
 The above specific statements are related just to requirements. Turning now
 to issues created in all phases in Figure~\ref{fig:raw},  we see that
 this data does not follow the exponential increase predicted
by the delayed issue effect:
\bi
\item There is much ``up and down'' in the chart, but no steady exponential growth such
as that see in, for example,  \fig{b81}.
\item The time in acceptance  testing is particularly low suggesting that few defects survived into testing
(and hence, there were few instances where code required massive rework).
\ei
%In summary:
%\bi
%\item
%The delayed issue effect has been reported in around a dozen papers, at least half of which date back to the 1970s. 
%\item
%But there is no trace of that  effect   in hundreds of software projects built  since 2006.
%\ei
%For illustrative purposes, the relative cost to fix errors per lifecycle phase in the TSP project data is overlayed with Boehm's cost curve~\cite{Boehm81} as well as the CCPDS-R case study~\cite{Royce98} in \fig{cost-to-fix-tsp}. Cost-to-fix for TSP is total time spent in each review, inspection, or test-related phase / \# of defects found in phase (reported in \fig{raw}). It is clear to see that the trend is relatively flat, closer to the pattern exhibited by the Royce case study (which also focused on early defect removal) than the exponential growth curve.

@@

Having documented the above issues, we assert that they are unlikely to be major issues in the study.
One of us (Nichols)
was closely associated with many of the projects in our sample. He is unaware of any frequent
use of exorbitantly expensive tools or people on these projects.

@@

\vspace*{0.5mm} 
\balance
\bibliographystyle{plain}
\bibliography{refs}
